Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40-90 MeV) on natural Nb

### 2018-02-17 nb_px_paper/nb_px_paper.tex
Started addressing hyphen/en-dash/em-dash usage, various comments.

\title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}% Force line breaks with \\
% \thanks{A footnote to the article title}%

@@

A stacked target of natural Nb, Cu, and Al thin foils were irradiated by 100 MeV protons at the Los Alamos National Laboratory's Isotope Production Facility.
The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new dosimetry standard for intermediate-energy protons.
A set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40.34 -- 89.74 MeV are presented in this work, as well as 5 independent measurements of isomer branching ratios.
Cross sections were measured using the well-characterized \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions  for accurate proton fluence measurement, with all activities quantified using high-purity germanium spectroscopy.
Variance minimization techniques were employed to reduce systematic uncertainties in proton energy and fluence, improving the reliability of these measurements. 
The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with improved precision compared with previous measurements.
This work reports the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40 - 90 MeV region.
Comparisons against the reaction modeling codes EMPIRE and TALYS are used to explore the impact of pre-equilibrium particle emission in the reaction dynamics for 40 - 90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.

@@

% Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator.
% The study was motivated by interest in the production of \ce{^{47}Sc} and \ce{^{64}Cu} as emerging medical isotopes.
% The cross sections were measured in ratio to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions on co-irradiated indium samples.
% Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 5\% uncertainty.
% The cross sections were determined with lower uncertainty than existing measurements and are found to be  in good agreement with both empirical and theoretical values.
% This work highlights the utility of using DD plasma-based neutron sources for a host of nuclear data measurements and potentially for the production of radionuclides for medical applications.

% \comment{Karl:  \enquote{Comment to engender some discussion.  I have a small concern here, reminiscent of what happened to our electron backstreaming paper in PRAB.  To be publishable, even in NIMB, there has to be a crisp research question resolved, or some innovation.  I think an angle that is missing here is that this is a new design of neutron generator, whose design maximizes the flux density (n/sec/cm2), although the total flux, while respectable, is not spectacular in itself.  This is Lee's recent mantra, and I now understand its significance.  Problematically, as Andrew has pointed out, we don't have the actual instrument paper published yet, so the thrust of the paper can't be too focused on the flux density issue, but a workable angle would be \enquote{given we have this new capability, this is an example of its power}.  Let me suggest Lee provide a sentence for the abstract, and a few sentences of text in the appropriate spot.}}

% \comment{The abstract is now nicely short and sweet, but should it be expanded at all?}

@@

Referring to abstract:
\comment{Stephen:  Not strictly true if you've omitted Na22 and Co56 from your fluence determination.  Update monitors here following discussion.}

\comment{Stephen: Unless you've already discussed this with co-authors, I would have someone from LANL (i.e. Meiring) instead or in addition.  Add one following discussion.}

\comment{Comment on the Si production here?}

\comment{Add CoH to codes also, and add extra physics language with Lee.}

@@

Figures of the cross sections measured in this work are presented here, in comparison with literature data \cite{Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}, the TENDL-2015 data library \cite{Koning2012}, and the reaction modeling codes EMPIRE-3.2.3 and TALYS-1.8 \cite{Herman2007,Koning2012}.

>>>>

\title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40-90 MeV) on natural Nb}% Force line breaks with \\
% \thanks{A footnote to the article title}%

@@

A stacked target of natural Nb, Cu, and Al thin foils were irradiated by 100 MeV protons at the Los Alamos National Laboratory's Isotope Production Facility.
The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new dosimetry standard for intermediate-energy protons.
A set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV are presented in this work, as well as 5 independent measurements of isomer branching ratios.
Cross sections were measured using the well-characterized 
% \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, 
\ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions  for accurate proton fluence measurement, with all activities quantified using high-purity germanium spectroscopy.
Variance minimization techniques were employed to reduce systematic uncertainties in proton energy and fluence, improving the reliability of these measurements. 
\textred{The \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, }
The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with improved precision compared with previous measurements.
This work reports the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    
% \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, 
\ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn} and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
Comparisons against the reaction modeling codes CoH$_3$, EMPIRE, and TALYS are used to explore the impact of pre-equilibrium particle emission in the reaction dynamics for 40--90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.

@@

@@

Referring to abstract:
% \comment{Stephen:  Not strictly true if you've omitted Na22 and Co56 from your fluence determination.  Update monitors here following discussion.}

\comment{Comment on the Si production here?  (see red text)}

\comment{Add extra physics language with Lee.}

@@

Figures of the cross sections measured in this work are presented here, in comparison with literature data \cite{Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}, the TENDL-2015 data library \cite{Koning2012}, and the reaction modeling codes CoH$_3$,EMPIRE-3.2.3, and TALYS-1.8 \cite{KAWANO2010,Herman2007,Koning2012}.

\comment{Add in CoH3 model output from Toshihiko to all plots}
